Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-03 inspiral_svd.tex
Removed author addresses
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@926 ccdd05d5-56c1-461a-bf98-85f6876523b4

\editorial{We have only Institution, City, State, Country for some co-authors.  Can we get rid of the full addresses, or is this at the discretion of the co-authors?  How about author e-mails?}
\address{$^1$ Canadian Institute for Theoretical Astrophysics, Toronto, ON,
Canada}
\address{$^2$  D\'{e}partement de physique, \'{E}cole Normale Sup\'{e}rieure de Cachan, 61
Avenue du Pr\'{e}sident Wilson, 94235 Cachan Cedex, France}
\address{$^3$ LIGO Laboratory - California Institute of Technology, Pasadena,
CA, USA} 
\address{$^4$ Facultat de F\'{i}sica, Universitat de Val\`{e}ncia, E-46100 Burjassot,
Spain} 
\address{$^5$ The University of Texas at Austin, Austin, TX, USA}
\address{$^6$ Perimeter Institute for Theoretical Physics, Waterloo, ON,
Canada} 
\address{$^7$ Department of Physics and Astronomy, Barnard College, Columbia
University, New York, NY 10027, USA} 
\address{$^8$ Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r
Gravitationphysik, Hannover, Germany} 
\address{$^9$ Leibniz Universit\"{a}t Hannover, Hannover, Germany}
\address{$^{10}$ Ryerson University, Toronto, ON, Canada}

>>>>

\address{$^1$ Canadian Institute for Theoretical Astrophysics, Toronto, ON,
Canada}
\address{$^2$  D\'{e}partement de physique, \'{E}cole Normale Sup\'{e}rieure de Cachan, Cachan, France}
\address{$^3$ LIGO Laboratory - California Institute of Technology, Pasadena,
CA, USA} 
\address{$^4$ Facultat de F\'{i}sica, Universitat de Val\`{e}ncia, Burjassot,
Spain} 
\address{$^5$ The University of Texas at Austin, Austin, TX, USA}
\address{$^6$ Perimeter Institute for Theoretical Physics, Waterloo, ON,
Canada} 
\address{$^7$ Department of Physics and Astronomy, Barnard College, Columbia
University, New York, NY, USA} 
\address{$^8$ Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r
Gravitationphysik, Hannover, Germany} 
\address{$^9$ Leibniz Universit\"{a}t Hannover, Hannover, Germany}
\address{$^{10}$ Ryerson University, Toronto, ON, Canada}
